Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-04-19 demystify.tex
updates

\paragraph{Not a good fit}  You could have an excellent profile, but if you are interested in a research area that the program does not have, you might not be admitted.
Similarly, if no faculty who is willing to advise you (e.g., they are on sabbatical or personal leave, do not have sufficient funding, or already have too many students already), you will not be admitted.  This is actually good for you, as you don't want to be in a program where no one can advise you.

@@

\paragraph{Low English exam scores (e.g., IELTS or TOEFL)}  While professors might not care much about these, there might be a certain minimum set by the college or the university that you need to pass to get admitted, especially for TA funding (e.g., you need to communicate well with students as a TA).  Thus, while professors are willing to argue for your case, they might be reluctant to go against the standard requirement of the university on English scores.  Note this is for international students, as domestic ones (or those from these \href{https://github.com/dynaroars/dynaroars.github.io/wiki/About-GMU#standard-tests-waiver-eligible-countries}{countries}) do not have to take these tests.

>>>>

\paragraph{Not a good fit}  You could have an excellent profile, but if you are interested in a research area that the program does not have, you might not be admitted.
Similarly, if no faculty who is willing to advise you (e.g., they are on sabbatical or personal leave, do not have sufficient funding, or already have too many students already), you will not be admitted.  This is good for you, as you don't want to be in a program where no one can advise you.

@@

\paragraph{Low English exam scores (e.g., IELTS or TOEFL)}  While profs. might not care much about these, there might be a certain minimum set by the college or the university that you need to pass to get admitted, especially for TA funding (e.g., you need to communicate well with students as a TA).  Thus, while professors are willing to argue for your case, they might be reluctant to go against the standard requirement of the university on English scores.  Note this is for international students, as domestic ones (or those from these \href{https://github.com/dynaroars/dynaroars.github.io/wiki/About-GMU#standard-tests-waiver-eligible-countries}{countries}) do not have to take these tests.
